---
title: "Comprehensive Powerpoint Slides"
author: "Thomas Gredig"
date: "5/25/2019"
output: 
  powerpoint_presentation:
    reference_doc: template.pptx
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

The comprehensive Powerpoint File contains the notes and data from a research project. It includes both positive and negative results; i.e. experimental questions that were explored and no answers, or negative answers were found. It includes details and graphs, analysis, and reviews of papers. 

The slides are not in order and the quality varies.

For the generation of the publication, the slides are arranged logically to build a story, and slides with non-essential content are skipped as determined to best fit with the story. However, other slides are kept for completeness of the record.



## RAW files

```{r, echo = FALSE}
path.source = '..'
if(file.exists('myConfig.R')) { source('myConfig.R') }
dir(path.source) -> file.list
num.files = length(file.list)
```

Looking through the RAW folder, we found `r num.files`.

- Number of VSM files: `r length(grep('VSM', file.list))`
- Number of XRD files: `r length(grep('XRD', file.list))`
- Number of AFM files: `r length(grep('AFM', file.list))`


## Ill-Formated RAW Files

```{r, echo=FALSE}

```

## XRD Graphs

```{r}
# remove.packages('rigakuXRD')
# devtools::install_github("thomasgredig/rigakuXRD")
library(rigakuXRD)
files.xrd = file.path(path.source, file.list[grep('XRD', file.list)])[1:5]
for(fn in files.xrd) {
  d <- xrd.read.TXTnoheader(fn)
  data = d[[1]]
  print(paste("Filaname:", fn))
  plot(data,log='y')
}
```
